Checkpoint 3

### 2020-04-20 Checkpoint3.Rmd
Update Checkpoint3.Rmd

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
abstract: ""
---

>>>>

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc:true
    toc_float:true
---
# Data
```{r}
save(states_cases_data, file = 'states_cases_data.RData')
dim(states_cases_data)
names(states_cases_data)
head(states_cases_data)
summary(states_cases_data)
```
